Trademap_Data_Analysis

### 2018-12-19 sourceCode/Analysis_Data_Muh_Clustering.Rmd
Update Analysis_Data_Muh_Clustering.Rmd

set.seed(20)
Cluster <- kmeans(Normalize_country_Cluster[, 2:6], 2, nstart = 20)

@@

>>>>

set.seed(20)
Cluster <- kmeans(Normalize_country_Cluster[, 2:6], 4, nstart = 20)

@@

```{r}
product_year<-export_Product_Group %>%
filter(Export_Value > 0) %>%
group_by(Product_Group_Name,year)%>%
summarise(Adet=n(), Toplam = sum(Export_Value))

product_Cluster <-dcast(product_year, Product_Group_Name ~ year , value.var = "Toplam") %>%
   rename(Toplam_2013 = "2013") %>%
   rename(Toplam_2014 = "2014") %>%
   rename(Toplam_2015 = "2015") %>%
   rename(Toplam_2016 = "2016") %>%
   rename(Toplam_2017 = "2017")

Normalize_product_Cluster<-product_Cluster%>%
mutate(normalized_2013 =  round((Toplam_2013  - mean(Toplam_2013))/sd(Toplam_2013 ),2)) %>%
mutate(normalized_2014 =  round((Toplam_2014  - mean(Toplam_2014))/sd(Toplam_2014 ),2)) %>%
mutate(normalized_2015 =  round((Toplam_2015  - mean(Toplam_2015))/sd(Toplam_2015 ),2)) %>%
mutate(normalized_2016 =  round((Toplam_2016  - mean(Toplam_2016))/sd(Toplam_2016 ),2)) %>%
mutate(normalized_2017 =  round((Toplam_2017  - mean(Toplam_2017))/sd(Toplam_2017 ),2)) %>%
select(Product_Group_Name,normalized_2013,normalized_2014,normalized_2015,normalized_2016,normalized_2017)

set.seed(20)
Cluster <- kmeans(Normalize_product_Cluster[, 2:6], 4, nstart = 20)

Normalize_product_Cluster$group<- as.factor(Cluster$cluster)

ggplot(Normalize_product_Cluster, aes(normalized_2013,normalized_2014, color = Normalize_product_Cluster$group)) + geom_point()
ggplot(Normalize_product_Cluster, aes(normalized_2014,normalized_2015, color = Normalize_product_Cluster$group)) + geom_point()
ggplot(Normalize_product_Cluster, aes(normalized_2015,normalized_2016, color = Normalize_product_Cluster$group)) + geom_point()

set.seed(20)
Cluster <- kmeans(product_Cluster[, 2:6], 4, nstart = 20)

product_Cluster$group<- as.factor(Cluster$cluster)

ggplot(product_Cluster, aes(Toplam_2013,Toplam_2014, color = product_Cluster$group)) + geom_point()
ggplot(product_Cluster, aes(Toplam_2014,Toplam_2015, color = product_Cluster$group)) + geom_point()
ggplot(product_Cluster, aes(Toplam_2015,Toplam_2016, color = product_Cluster$group)) + geom_point()
ggplot(product_Cluster, aes(Toplam_2016,Toplam_2017, color = product_Cluster$group)) + geom_point()
